An Embedding Framework for Consistent Polyhedral Surrogates

### 2021-06-18 poly-embed-journal/poly-embed-journal.tex
Starting to iterate on phase 2

\begin{itemize}\setlength{\itemsep}{0pt}
\item Define $\V = L(\R) \subseteq \reals^\Y_+$ and $\H_{\V} = \{H_v^+ \mid v\in\V\}$.  Unlike above, these could be infinite sets.
\item Let $\H = \H_\Y \cup \H_{\V}$.
\begin{claim}
	$G = \cap\H$ by definition of $\risk{L}$ \raf{prove}
\end{claim}
\begin{proof}
  \raf{Let $(x,c) \in G$.  Show $(x,c)\in\cap \H$.  Then vice versa.  Or maybe iff once you get the hang of it.}

  $\implies$
  Have $g(x) \geq c$... use $g=\risk{L}_+$... then for all loss vectors $v = L()$, $(x,c) \in H_v^+$.  Done.

  Other dir: for any $(x,c) \in \cap \H$
	\jessie{If $\H$ is redundant, there is still a finite $\H^*$ such that $\H^* \subseteq \H$... right?  weird if $\H$ is infinite.}
\end{proof}
\item Need to use minimizable
\begin{claim}
	Argue that $\H_{\V^*} \subseteq \H$, since $\H_\Y \cup \H_{\V^*}$ is the unique min H-rep of $G$. \raf{not sure how to do this, since $\H$ could be infinite}
\end{claim}
\item 
\begin{corollary}
	Conclude there is some set $\R^* \subseteq \R$ such that $L(\R^*) = \V^*$ (without duplicates).
\end{corollary}
\item 
\begin{claim} 
For all $v\in\reals^\Y_+$, if $H_v$ supports $G$,  $\dim(\pi(F_v)) = \dim(F_v)-1$.
\end{claim}
\item Let $r$ be a report, and let $\hat v = L(r)$.
\item As $H_{\hat v}^+ \in \H$, it supports $G$ or it is redundant in $\H$ (or both).
\item If it does support $G$, then $F_{\hat v} = H_{\hat v}^+ \cap G$ is a face of $G$, and thus a subset of a facet.
\item Argue that $F_{\hat v}$ must be a subset of one of the $\V^*$ facets $F_v$ (as opposed to the vertical ones)
\item Thus, $\pi(F_{\hat v}) \subseteq \pi(F_v)$. \raf{This will show (3) once we translate back}
\item Claim: $\R'$ is a rep set for $L$ if and only if $\V \subseteq L(\R')$.
\item Corollary: $\R^*$ is a min rep set for $L$ if and only if $\V^* = L(\R^*)$. \raf{(1)}
\end{itemize}

>>>>

\begin{itemize}\setlength{\itemsep}{0pt}
\item Define $\V = L(\R) \subseteq \reals^\Y_+$ and $\H_{\V} = \{H_v^+ \mid v\in\V\}$.  Unlike above, these could be infinite sets.
\item Let $\H = \H_\Y \cup \H_{\V}$.
\end{itemize}
\begin{claim}
	$G = \cap\H$ by definition of $\risk{L}_+$.
\end{claim}
\begin{proof}
%  \raf{Let $(x,c) \in G$.  Show $(x,c)\in\cap \H$.  Then vice versa.  Or maybe iff once you get the hang of it.}
%  $(x,c) \in G = \{(x,c) \mid g(x) \geq c\}$.
%  Since $g(x) = \risk L_+(x)$, we then have $\min_{v \in \V}\inprod{x}{v} - \delta(x \mid \reals^\Y_+) = \inf_{r \in \R} \inprod{x}{L(r)}$\jessie{minnable doesn't really come in here, but want to be careful}.
%  Thus, for all loss vectors such that $v = L(r)$ we have $\inprod{v}{x} = \inprod{L(r)}{x} \geq c$, and therefore $(x,c) \in H^+_v$ for all $v \in L(\R)$, and is therefore in the intersection $H_v^+$.

  Observe that $x \in \reals^Y_+ \iff (x, c) \in \cap \H_\Y$.
  Moreover,
  \begin{align*}
  (x,c) \in G &\iff g(x) \geq c \\
  &\iff \inprod{v}{x} \geq c \,\, \forall v \in \V \\
  &\iff (x,c) \in H^+_{v} \,\, \forall v \in L(\R) \\
  &\iff \inprod{L(r)}{x} \geq c \,\, \forall r \in \R\\
  &\iff (x,c) \in H^+_{L(r)} \,\, \forall r \in \R \\
  &\iff (x,c) \in \cap \H_\V \\ 
  \end{align*}
  Combining the two equalities, we have $G = \cap \H$.

%  $\implies$
%  Have $g(x) \geq c$... use $g=\risk{L}_+$... then for all loss vectors $v = L()$, $(x,c) \in H_v^+$.  Done.
%
%  Other dir: for any $(x,c) \in \cap \H$
\end{proof}

Need to use minimizable
Take $\V^*$ to be the unique finite set such that $\H^* = \H_\Y \cup \H_{\V^*}$, where $\H^*$ is the unique minimum halfspace representation for $G$ as in phase 1.

\begin{claim}
	$\H_{\V^*} \subseteq \H$
\end{claim}
\begin{proof}
	$\H_{\V^*} \subseteq \H^* \subseteq \H$.
	The first subset inclusion follows by construction of $\H_{\V^*}$, and the second follows from \jessie{cite} as $\H^*$ is the unique minimum halfspace representation of $G$, and is finite.
	%%$G = \cap \H^*$ and $\H_{\V^*} \subseteq \H$.
	%since $\H_\Y \cup \H_{\V^*}$ is the unique min H-rep of $G$. \raf{not sure how to do this, since $\H$ could be infinite}
\end{proof}

\begin{corollary}
	There is a set $\R^* \subseteq \R$ such that $L(\R^*) = \V^*$ (without duplicates).
\end{corollary}

\begin{claim} 
For all $v\in\reals^\Y_+$, if $H_v$ supports $G$,  $\dim(\pi(F_v)) = \dim(F_v)-1$.
\end{claim}
\begin{proof}
	\jessie{TODO}
	$F_v = \H_v \cap G \neq \emptyset$ by assumption.
	$\dim(F_v) = \dim(\affhull(F_v))$
	$\dim(\pi(F_v)) = \dim(F_v) - 1$.
\end{proof}

Let $r$ be a report, and let $v = L(r)$.
As $H_{v}^+ \in \H$, it supports $G$ or it is redundant in $\H$ (or both).

\begin{claim}If a $H_v \in \H$ does support $G$, then $F_{v} = H_{v} \cap G$ is a face of $G$, and thus a subset of a facet.
\end{claim}
\begin{claim}
	For any $v \in \V$, the face $F_{v}$ must be a subset of one of the $\V^*$ facets $F_{v^*}$ (as opposed to the vertical ones)
\end{claim}
\begin{claim}
	Thus, $\pi(F_{\hat v}) \subseteq \pi(F_v)$. \raf{This will show (3) once we translate back}
\end{claim}
\begin{claim}
	$\R'$ is a rep set for $L$ if and only if $\V \subseteq L(\R')$.
\end{claim}
\begin{corollary}
	$\R^*$ is a min rep set for $L$ if and only if $\V^* = L(\R^*)$. \raf{(1)}
\end{corollary}
